Contract Orchestration for OCaml \\ Progress Report

### 2022-09-20 reports/2022-09-06/COOC-report.tex
update report

Doan and Thiemann have worked on the type-safe interaction with the Tezos blockchain, distributed verification of assertions, and contract modules, and a checker for Michelson smart contracts on various aspects.
\paragraph{December 2021: Presentation at APLAS Conferece}

\begin{itemize}
\item Thiemann gave a talk at the Asian Symposium on Programming Languages and Systems (APLAS 2021) (remotely due to the Covid situation). The talk is based on our paper on a typed programmatic interface to contracts on the blockchain, in which we propose a typed API for creating and invoking contracts and querying the state of the Tezos blockchain along with an operational semantics for functional programs running alongside smart contracts on a blockchain. During the talk, we got some suggestions that helped to improve our Tezos API.

\paragraph{September 2021 - June 2022: Distributed  Assertion Checking}
\begin{itemize}
\item Research on distributed assertion checking for smart contracts was conducted by two students, Tamara Bernhardt and Julian Veigel, as part of their master's thesis, with Tamara defining the grammar for the assertion language and Julian presenting different approaches and discussing their strengths and weaknesses. However, the approaches proposed by Tamara and Julian require changes  in the backend system (Tezos and Etherum). We therefore worked on a solution so that the approach can work without changes to the backend system.
\item 
The basic idea is to distribute the validation process among several nodes in the network, all testing different property cases. The goal is to reduce costs while preserving fundamental properties such as decentralization and trust. The senior is as follows. A caller submits a parameter to the blockchain that needs to be validated. The parameter is then forwarded to all nodes as validators in the network, which then validate it. After the parameter is validated, the actual work that uses the parameter is executed. The idea behind our approach is that validation is done outside the chain, but the result of this process is then checked inside the chain. To check the validity of a parameter, each validator independently performs an off-chain assertion, which is the same as the one used in the on-chain validation assertion. The result is then submitted to the blockchain, which then uses the on-chain assertion to verify the submission. The off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
\item We define a domain specific language (DSL) to express assertions. The main actor in our method is the on/off assertion contracts. We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our DSL. The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Michelson (Solidity). To perform the conversion automatically, we constrain the semantics of the DSL. So far, we have done:
\begin{itemize}
\item completing the design and implementation of a DSL to express the assertion (reused Tamara work).
\item proposing an algorithm to automatically convert an assertion to the on/off-chain smart contract.
\end{itemize}
\end{itemize}

@@

\begin{itemize}
\item We proposed a symbolic execution model for Michelson that allows us to ensure type-safe invocation of the contract on the blockchain. Namely, the model allows us to express the pre- and post-conditions and then specify invariants. In addition, we can use the model to impose constraints on the possible call orders of the entrypoints.
\item Thiemann implemented a symbolic execution for Michelson in Ocaml. Given a symbolic specification of an entrypoint, the symbolic execution returns the set of final states with the bundle of path conditions. 
\item Given an invocation of a smart contract, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation may be succeed. 
\item The verification of invariants and constraints can be done using an SMT solver. For this purpose, we exploded the Z3 solver and its library into Ocaml.
\end{itemize}

@@

\item The typed Tezos API is completely implemented.
\item a symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
\end{itemize}

>>>>

Doan and Thiemann have worked on various aspects of type-safe interaction with the Tezos blockchain, distributed verification of assertions and contract modules, and a checker for Michelson smart contracts.

\paragraph{December 2021: Presentation at APLAS Conferece}

\begin{itemize}
\item Thiemann gave a talk at the Asian Symposium on Programming Languages and Systems (APLAS 2021) (remote due to the Covid situation). The talk is based on our paper on a typed programmatic interface to contracts on the blockchain, in which we propose a typed API for creating and invoking contracts and querying the state of the Tezos blockchain, along with operational semantics for functional programs running alongside smart contracts on a blockchain. During the talk, we received some suggestions that helped us improve our Tezos API.
\end{itemize}

\paragraph{September 2021 - June 2022: Distributed  Assertion Checking}
\begin{itemize}
\item Research on distributed assertion checking for smart contracts was conducted by two students, Tamara Bernhardt and Julian Veigel, as part of their master's thesis, with Tamara defining the grammar for the assertion language and Julian presenting different approaches and discussing their strengths and weaknesses. However, the approaches proposed by Tamara and Julian require changes  in the backend system (Tezos and Etherum). We therefore worked on a solution so that the approach can work without changes to the backend system.
\item 
The basic idea is to distribute the validation process among several nodes in the network, all testing different property cases. The goal is to reduce costs while preserving fundamental properties such as decentralization and trust. The senior is as follows. A caller submits a parameter to the blockchain that needs to be validated. The parameter is then forwarded to all nodes as validators in the network, which then validate it. After the parameter is validated, the actual work that uses the parameter is executed. The idea behind our approach is that validation is done outside the chain, but the result of this process is then checked inside the chain. 
\item To check the validity of a parameter, each validator independently performs an off-chain assertion, which is the same as the one used in the on-chain assertion. The result of the calculation can be
a counterexample, an award computational proof, or a non-award computational
proof. The result is then submitted to the blockchain, which then uses the on-chain assertion to verify the submission. The on/off-chain assertion contains the negation formulas of the assertion for parameters and takes a seed and a parameter as input.
\item We define a assertion domain specific language (ADSL) to express assertions. The main actor in our method is the on/off-chain assertion contracts. We propose an algorithm to automatically generate the on/off-chain assertion contract from an assertion written in our ADSL. The algorithm is then implemented as a converter that takes the AST of an assertion after the parser (or the AST for its negation after the transformer step) and returns the on/off-chain assertion contract written in Michelson (Solidity). To perform the conversion automatically, we constrain the semantics of the ADSL. So far, we have done:
\begin{itemize}
\item completed the design and implementation of a ADSL to express the assertion (reused Tamara work).
\item proposed an algorithm to automatically convert an assertion  written in ADSL to the on/off-chain assertion.
\end{itemize}
\end{itemize}

@@

\begin{itemize}
\item We have proposed a symbolic execution model for Michelson that allows us to ensure safe invocations of a contract on the blockchain. The model allows us to express preconditions and postconditions and then specify invariants and constraints that are then used to ensure a secure invocation. We can also use the model to constrain the possible call sequences of the entrypoints.
\item Thiemann implemented a symbolic execution for Michelson in Ocaml. Given a symbolic specification of an entrypoint, the symbolic execution returns the set of final states with the bundle of path conditions. 
\item Given an invocation of a smart contract, the invocation can be checked against these invariants and constraints before being used in the chain, where the invocation may be succeed. 
\item The verification of invariants and constraints can be done using an SMT solver. For this purpose, we exploded the Z3 solver and its library into Ocaml.
\end{itemize}

@@

\item The typed Tezos API is completely implemented.
\item The ADSL for specifying assertions for distributed checking and an alorithm to deploy the assertion on the blockchain system (Tezos and Ethereum).
\item a symbolic execution model for Michelson that allows us to specify pre-conditions, post-conditions, and allowable call sequences for entrypoints; 
\end{itemize}
